---
title: "R Markdown and Leaflet"
author: "Bo Kaplan"
date: "October 29, 2019"
output: html_notebook
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

Leaflet is one of the most popular Javascript libraries for creating interactive maps. The leaflet R package allows you to create your own leaflet maps without needing to know any Javascript!

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## My First Map

The `leaflet()` function creates a map widget that you can store in a variable so that you can modify the map later on. You can add features to the map using the pipe operator (`%>%`) just like in dplyr. The `addTiles()` function adds mapping data from Open Street Map. You can also add markers to your map one at a time using the `addMarkers()` function by specifying the longitude and latitude. (Here's a tip if you tend to mix them up.) You can specify popup text for when you click on the marker with the `popup` argument. For this map, I've decided I'll dream about eating at my favorite sub shop.

```{r}
library(leaflet)

my_map <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=43.198486, lng=-77.582458, popup="Rubino's Italian Foods - My Favorite Sub Shop")
```

```{r my_map}
my_map
```



